Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-11 article/article.tex
Commit 2024-06-11 22:14

!!! monthly weithe !!!

Another interesting aspect of the CE events is their distribution within
the year. Figure\nobreakspace{}\ref{fig:relative-month-occurrences}
shows the monthly box and whisker plot of the CE number of occurrence
normalized with the highest median value, that occurs on June. Although
the number of occurrences has a wide spread throughout the study period,
the most active period of CE occurrences is during May and June. During
the Winter (December -- February) the CE cases are about \(25\,\%\) of
the maximum. For the rest months, the occurrences gradually ramp between
the maximum and minimum. This seasonality is a combinations of the
clouds occurrences, and the relevant position of the sun during each
season of the year. Unfortunately, the lack of detailed data on cloud
formation, type and location is not allowing further analysis.

>>>>

!!! monthly weigth !!!

Another interesting aspect of the CE events is their distribution within
the year. Figure\nobreakspace{}\ref{fig:relative-month-occurrences}
shows the monthly box and whisker plot of the CE number of occurrence
normalized with the highest median value, that occurs on June. Although
CE events are present throughout the year, the most active period is
during May and June. During the winter (December -- February) the number
of CE cases is about \(25\,\%\) of the maximum. For the rest months, the
occurrences gradually ramp between the maximum and minimum. This
seasonality is a combinations of the clouds occurrences, and the
relevant position of the sun during each season of the year.
Unfortunately, the lack of detailed data on cloud formation, type and
location is not allowing further analysis.
